### 2018-05-01 doc/paper.tex
Removing dummy "Quotes" section.
Also

- Removing the Bezerra13 paper from bibliography (it certainly
  wasn't needed)
- Adding the other two papers about Bernstein evaluation to the
  Farouki reference (i.e. they are just supporting the fact that
  the de Casteljau algorithm is not so bad)
- Moving all `label`-s after `caption` when relevant (this was
  confusing `pdflatex`)
- Making sure the bibliography shows up in the TOC

\usepackage{amsthm,amssymb,amsmath}
%% H/T: https://tex.stackexchange.com/a/202168/32270
\usepackage{textcomp}
%% H/T: https://tex.stackexchange.com/a/56877/32270
\usepackage{algorithm}
\usepackage{algpseudocode}
%% H/T: https://tex.stackexchange.com/a/244805
\usepackage{booktabs,siunitx}
%% H/T: https://tex.stackexchange.com/a/4217/32270
\usepackage{mathtools}
%% H/T: https://tex.stackexchange.com/a/33869/32270
\makeatletter
\newenvironment{breakablealgorithm}
  {% \begin{breakablealgorithm}
   \begin{center}
     \refstepcounter{algorithm}% New algorithm
     \hrule height.8pt depth0pt \kern2pt% \@fs@pre for \@fs@ruled
     \renewcommand{\caption}[2][\relax]{% Make a new \caption
       {\raggedright\textbf{\ALG@name~\thealgorithm} ##2\par}%
       \ifx\relax##1\relax % #1 is \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##2}%
       \else % #1 is not \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##1}%
       \fi
       \kern2pt\hrule\kern2pt
     }
  }{% \end{breakablealgorithm}
     \kern2pt\hrule\relax% \@fs@post for \@fs@ruled
   \end{center}
  }
\makeatother
%% H/T: https://tex.stackexchange.com/a/202047/32270
%%      https://tex.stackexchange.com/a/32463/32270
\usepackage[labelfont=bf]{caption}

@@

In computer aided geometric design, polynomials are usually expressed in
Bernstein form. Polynomials in this form are usually evaluated by the
de Casteljau algorithm. This algorithm has a round-off error bound
which grows only linearly with degree, even though the number of
arithmetic operations grows quadratically. The Bernstein basis is
optimally suited (\cite{Farouki1987}) for polynomial evaluation; it is
typically more accurate than the monomial basis, for example in
Figure~\ref{fig:horner-inferior} evaluation via Horner's method produces
a jagged curve for points near a triple root, but the de Casteljau algorithm
produces a smooth curve. Nevertheless the de Casteljau
algorithm returns results arbitrarily less accurate than the working
precision \(\mach\) when evaluating \(p(s)\) is ill-conditioned.
The relative accuracy of the computed
evaluation with the de Casteljau algorithm (\texttt{DeCasteljau}) satisfies
(\cite{Mainar1999}) the following a priori bound:
\begin{equation}\label{de-casteljau-error}
  \frac{\left|p(s) - \mathtt{DeCasteljau}(p, s)\right|}{\left|p(s)\right|} \leq
  \cond{p, s} \times \mathcal{O}(\mach).
\end{equation}
In the right-hand side of this inequality, \(\mach\) is the computing
precision and the condition number \(\cond{p, s} \geq 1\) only depends
on \(s\) and the Bernstein coefficients of \(p\) --- its expression will
be given further.

@@

\begin{figure}\label{fig:loc-err-accumulate}
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
  \node (b0) {\(\widehat{b}^{(n)}\)}
    child {node (b1) {\(\widehat{b}^{(n - 1)}\)}
      child {node (b2) {\(\widehat{b}^{(n - 2)}\)}
        child {node (bdots) {\(\vdots\)}
          child {node (bn) {\(\widehat{b}^{(0)}\)}}
          child {node (ln) {\(\ell^{(0)}\)}}
        }
        child {node (ldots) {\(\vdots\)}}
      }
      child {node (l2) {\(\ell^{(n - 2)}\)}}
    }
    child {node (l1) {\(\ell^{(n - 1)}\)}};
  %%
  \path (b1) -- (l1) node [midway] {\(+\)};
  \path (b2) -- (l2) node [midway] {\(+\)};
  \path (bn) -- (ln) node [midway] {\(+\)};
  %% eb == exact b
  \node [right of=b0] (eb0) {\(b^{(n)}\)}
    child {node (eb1) {\(b^{(n - 1)}\)}
      child {node (eb2) {\(b^{(n - 2)}\)}
        child {node (ebdots) {\(\vdots\)}
          child {node (ebn) {\(b^{(0)}\)}}
        }
      }
    };
\end{tikzpicture}
\captionsetup{width=.75\linewidth}
\caption{Local round-off errors}
\end{figure}

@@

\begin{breakablealgorithm}\label{alg:comp-de-casteljau}
  \caption{\textit{Compensated de Casteljau algorithm for polynomial evaluation.}}

@@

\begin{figure}\label{fig:error-filtration}
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
    \node [box] (bj) {\(b\)};
    \node [box, below of=bj] (bn0) {\(\widehat{b}^{(n)}\)};
    \node [box, right of=bn0] (dbn0) {\(\widehat{\partial b}^{(n)}\)};
    \node [box, right of=dbn0] (ddbn0) {\(\widehat{\partial^2 b}^{(n)}\)};
    \node [box, right of=ddbn0] (dddbn0) {\(\widehat{\partial^3 b}^{(n)}\)};
    %%
    \node [box, below of=bn0] (bn1) {\(\widehat{b}^{(n - 1)}\)};
    \node [box, below of=dbn0] (dbn1) {\(\widehat{\partial b}^{(n - 1)}\)};
    \node [box, below of=ddbn0] (ddbn1) {\(\widehat{\partial^2 b}^{(n - 1)}\)};
    \node [box, below of=dddbn0] (dddbn1) {\(\widehat{\partial^3 b}^{(n - 1)}\)};
    %%
    \node [box, below of=bn1] (bn2) {\(\widehat{b}^{(n - 2)}\)};
    \node [box, below of=dbn1] (dbn2) {\(\widehat{\partial b}^{(n - 2)}\)};
    \node [box, below of=ddbn1] (ddbn2) {\(\widehat{\partial^2 b}^{(n - 2)}\)};
    \node [box, below of=dddbn1] (dddbn2) {\(\widehat{\partial^3 b}^{(n - 2)}\)};
    %%
    \path [line] (bn0) -- node[above] {\(\widehat{\ell}_1^{(n)}\)} (dbn0);
    \path [line] (dbn0) -- node[above] {\(\widehat{\ell}_2^{(n)}\)} (ddbn0);
    \path [line] (ddbn0) -- node[above] {\(\widehat{\ell}_3^{(n)}\)} (dddbn0);
    \node [empty-box, right of=dddbn0] (right0) {\(\cdots\)};
    \path [line] (dddbn0) -- node[above] {\(\widehat{\ell}_4^{(n)}\)} (right0);
    %%
    \path [line] (bn1) -- node[above] {\(\widehat{\ell}_1^{(n - 1)}\)} (dbn1);
    \path [line] (dbn1) -- node[above] {\(\widehat{\ell}_2^{(n - 1)}\)} (ddbn1);
    \path [line] (ddbn1) -- node[above] {\(\widehat{\ell}_3^{(n - 1)}\)} (dddbn1);
    \node [empty-box, right of=dddbn1] (right1) {\(\cdots\)};
    \path [line] (dddbn1) -- node[above] {\(\widehat{\ell}_4^{(n - 1)}\)} (right1);
    %%
    \path [line] (bn2) -- node[above] {\(\widehat{\ell}_1^{(n - 2)}\)} (dbn2);
    \path [line] (dbn2) -- node[above] {\(\widehat{\ell}_2^{(n - 2)}\)} (ddbn2);
    \path [line] (ddbn2) -- node[above] {\(\widehat{\ell}_3^{(n - 2)}\)} (dddbn2);
    \node [empty-box, right of=dddbn2] (right2) {\(\cdots\)};
    \path [line] (dddbn2) -- node[above] {\(\widehat{\ell}_4^{(n - 2)}\)} (right2);
    %%
    \path [line] (bj) -- (bn0);
    \path [line] (bn0) -- node[fill=white] {\(U_n(s)\)} (bn1);
    \path [line] (bn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (bn2);
    \node [empty-box-vert, below of=bn2] (bottom0) {\(\vdots\)};
    \path [line] (bn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom0);
    %%
    \path [line] (dbn0) -- node[fill=white] {\(U_n(s)\)} (dbn1);
    \path [line] (dbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dbn2);
    \node [empty-box-vert, below of=dbn2] (bottom1) {\(\vdots\)};
    \path [line] (dbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom1);
    %%
    \path [line] (ddbn0) -- node[fill=white] {\(U_n(s)\)} (ddbn1);
    \path [line] (ddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (ddbn2);
    \node [empty-box-vert, below of=ddbn2] (bottom2) {\(\vdots\)};
    \path [line] (ddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom2);
    %%
    \path [line] (dddbn0) -- node[fill=white] {\(U_n(s)\)} (dddbn1);
    \path [line] (dddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dddbn2);
    \node [empty-box-vert, below of=dddbn2] (bottom3) {\(\vdots\)};
    \path [line] (dddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom3);
\end{tikzpicture}
\captionsetup{width=.75\linewidth}
\caption{Filtering errors}
\end{figure}

@@

\begin{breakablealgorithm}\label{alg:k-comp-de-casteljau}
  \caption{\(K\)-\textit{compensated de Casteljau algorithm.}}

@@

\section{Quotes: Selection of Test Cases}

From \cite{Delgado2015} (end of Section 3):

\begin{quote}
  We can observe that, in this case, the algorithm with a good
  behavior everywhere is the de Casteljau algorithm
\end{quote}

\noindent In the same paper (when referring to \cite{Bezerra2013} at the
beginning of Section 2):

\begin{quote}
  assuming that all control points are positive. This assumption avoided
  ill-conditioned polynomials. In this section, we shall show that this is
  a natural assumption in Computer Aided Geometric Design (from now on,
  C.A.G.D.) and that it permits to assure high relative precision for the
  evaluation through a large family of representations in C.A.G.D.
\end{quote}

\noindent From the same author, in \cite{Mainar2005} (towards the
end of Section 5, at the bottom of page 109):

\begin{quote}
  Let us observe that in this case, the de Casteljau algorithm presents
  better stability properties for the evaluation near the roots. In fact,
  the de Casteljau algorithm has good behaviour even when using simple
  precision, although the running error bound is not so accurate in points
  close to the roots.
\end{quote}

@@

\begin{breakablealgorithm}\label{alg:two-prod-fma}
  \caption{\textit{EFT of the sum of two floating point numbers with a FMA.}}

>>>>

\usepackage{amsthm,amssymb,amsmath}
%% H/T: https://tex.stackexchange.com/a/202168/32270
\usepackage{textcomp}
%% H/T: https://tex.stackexchange.com/a/56877/32270
\usepackage{algorithm}
\usepackage{algpseudocode}
%% H/T: https://tex.stackexchange.com/a/244805
\usepackage{booktabs,siunitx}
%% H/T: https://tex.stackexchange.com/a/4217/32270
\usepackage{mathtools}
%% H/T: https://tex.stackexchange.com/a/33869/32270
\makeatletter
\newenvironment{breakablealgorithm}
  {% \begin{breakablealgorithm}
   \begin{center}
     \refstepcounter{algorithm}% New algorithm
     \hrule height.8pt depth0pt \kern2pt% \@fs@pre for \@fs@ruled
     \renewcommand{\caption}[2][\relax]{% Make a new \caption
       {\raggedright\textbf{\ALG@name~\thealgorithm} ##2\par}%
       \ifx\relax##1\relax % #1 is \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##2}%
       \else % #1 is not \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##1}%
       \fi
       \kern2pt\hrule\kern2pt
     }
  }{% \end{breakablealgorithm}
     \kern2pt\hrule\relax% \@fs@post for \@fs@ruled
   \end{center}
  }
\makeatother
%% H/T: https://tex.stackexchange.com/a/202047/32270
%%      https://tex.stackexchange.com/a/32463/32270
\usepackage[labelfont=bf]{caption}
%% H/T: https://tex.stackexchange.com/a/71153/32270
\usepackage[nottoc,notlot,notlof]{tocbibind}

@@

In computer aided geometric design, polynomials are usually expressed in
Bernstein form. Polynomials in this form are usually evaluated by the
de Casteljau algorithm. This algorithm has a round-off error bound
which grows only linearly with degree, even though the number of
arithmetic operations grows quadratically. The Bernstein basis is
optimally suited (\cite{Farouki1987}, \cite{Delgado2015}, \cite{Mainar2005})
for polynomial evaluation; it is
typically more accurate than the monomial basis, for example in
Figure~\ref{fig:horner-inferior} evaluation via Horner's method produces
a jagged curve for points near a triple root, but the de Casteljau algorithm
produces a smooth curve. Nevertheless the de Casteljau
algorithm returns results arbitrarily less accurate than the working
precision \(\mach\) when evaluating \(p(s)\) is ill-conditioned.
The relative accuracy of the computed
evaluation with the de Casteljau algorithm (\texttt{DeCasteljau}) satisfies
(\cite{Mainar1999}) the following a priori bound:
\begin{equation}\label{de-casteljau-error}
  \frac{\left|p(s) - \mathtt{DeCasteljau}(p, s)\right|}{\left|p(s)\right|} \leq
  \cond{p, s} \times \mathcal{O}(\mach).
\end{equation}
In the right-hand side of this inequality, \(\mach\) is the computing
precision and the condition number \(\cond{p, s} \geq 1\) only depends
on \(s\) and the Bernstein coefficients of \(p\) --- its expression will
be given further.

@@

\begin{figure}
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
  \node (b0) {\(\widehat{b}^{(n)}\)}
    child {node (b1) {\(\widehat{b}^{(n - 1)}\)}
      child {node (b2) {\(\widehat{b}^{(n - 2)}\)}
        child {node (bdots) {\(\vdots\)}
          child {node (bn) {\(\widehat{b}^{(0)}\)}}
          child {node (ln) {\(\ell^{(0)}\)}}
        }
        child {node (ldots) {\(\vdots\)}}
      }
      child {node (l2) {\(\ell^{(n - 2)}\)}}
    }
    child {node (l1) {\(\ell^{(n - 1)}\)}};
  %%
  \path (b1) -- (l1) node [midway] {\(+\)};
  \path (b2) -- (l2) node [midway] {\(+\)};
  \path (bn) -- (ln) node [midway] {\(+\)};
  %% eb == exact b
  \node [right of=b0] (eb0) {\(b^{(n)}\)}
    child {node (eb1) {\(b^{(n - 1)}\)}
      child {node (eb2) {\(b^{(n - 2)}\)}
        child {node (ebdots) {\(\vdots\)}
          child {node (ebn) {\(b^{(0)}\)}}
        }
      }
    };
\end{tikzpicture}
\captionsetup{width=.75\linewidth}
\caption{Local round-off errors}
\label{fig:loc-err-accumulate}
\end{figure}

@@

\begin{breakablealgorithm}
  \caption{\textit{Compensated de Casteljau algorithm for polynomial evaluation.}}
  \label{alg:comp-de-casteljau}

@@

\begin{figure}
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
    \node [box] (bj) {\(b\)};
    \node [box, below of=bj] (bn0) {\(\widehat{b}^{(n)}\)};
    \node [box, right of=bn0] (dbn0) {\(\widehat{\partial b}^{(n)}\)};
    \node [box, right of=dbn0] (ddbn0) {\(\widehat{\partial^2 b}^{(n)}\)};
    \node [box, right of=ddbn0] (dddbn0) {\(\widehat{\partial^3 b}^{(n)}\)};
    %%
    \node [box, below of=bn0] (bn1) {\(\widehat{b}^{(n - 1)}\)};
    \node [box, below of=dbn0] (dbn1) {\(\widehat{\partial b}^{(n - 1)}\)};
    \node [box, below of=ddbn0] (ddbn1) {\(\widehat{\partial^2 b}^{(n - 1)}\)};
    \node [box, below of=dddbn0] (dddbn1) {\(\widehat{\partial^3 b}^{(n - 1)}\)};
    %%
    \node [box, below of=bn1] (bn2) {\(\widehat{b}^{(n - 2)}\)};
    \node [box, below of=dbn1] (dbn2) {\(\widehat{\partial b}^{(n - 2)}\)};
    \node [box, below of=ddbn1] (ddbn2) {\(\widehat{\partial^2 b}^{(n - 2)}\)};
    \node [box, below of=dddbn1] (dddbn2) {\(\widehat{\partial^3 b}^{(n - 2)}\)};
    %%
    \path [line] (bn0) -- node[above] {\(\widehat{\ell}_1^{(n)}\)} (dbn0);
    \path [line] (dbn0) -- node[above] {\(\widehat{\ell}_2^{(n)}\)} (ddbn0);
    \path [line] (ddbn0) -- node[above] {\(\widehat{\ell}_3^{(n)}\)} (dddbn0);
    \node [empty-box, right of=dddbn0] (right0) {\(\cdots\)};
    \path [line] (dddbn0) -- node[above] {\(\widehat{\ell}_4^{(n)}\)} (right0);
    %%
    \path [line] (bn1) -- node[above] {\(\widehat{\ell}_1^{(n - 1)}\)} (dbn1);
    \path [line] (dbn1) -- node[above] {\(\widehat{\ell}_2^{(n - 1)}\)} (ddbn1);
    \path [line] (ddbn1) -- node[above] {\(\widehat{\ell}_3^{(n - 1)}\)} (dddbn1);
    \node [empty-box, right of=dddbn1] (right1) {\(\cdots\)};
    \path [line] (dddbn1) -- node[above] {\(\widehat{\ell}_4^{(n - 1)}\)} (right1);
    %%
    \path [line] (bn2) -- node[above] {\(\widehat{\ell}_1^{(n - 2)}\)} (dbn2);
    \path [line] (dbn2) -- node[above] {\(\widehat{\ell}_2^{(n - 2)}\)} (ddbn2);
    \path [line] (ddbn2) -- node[above] {\(\widehat{\ell}_3^{(n - 2)}\)} (dddbn2);
    \node [empty-box, right of=dddbn2] (right2) {\(\cdots\)};
    \path [line] (dddbn2) -- node[above] {\(\widehat{\ell}_4^{(n - 2)}\)} (right2);
    %%
    \path [line] (bj) -- (bn0);
    \path [line] (bn0) -- node[fill=white] {\(U_n(s)\)} (bn1);
    \path [line] (bn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (bn2);
    \node [empty-box-vert, below of=bn2] (bottom0) {\(\vdots\)};
    \path [line] (bn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom0);
    %%
    \path [line] (dbn0) -- node[fill=white] {\(U_n(s)\)} (dbn1);
    \path [line] (dbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dbn2);
    \node [empty-box-vert, below of=dbn2] (bottom1) {\(\vdots\)};
    \path [line] (dbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom1);
    %%
    \path [line] (ddbn0) -- node[fill=white] {\(U_n(s)\)} (ddbn1);
    \path [line] (ddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (ddbn2);
    \node [empty-box-vert, below of=ddbn2] (bottom2) {\(\vdots\)};
    \path [line] (ddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom2);
    %%
    \path [line] (dddbn0) -- node[fill=white] {\(U_n(s)\)} (dddbn1);
    \path [line] (dddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dddbn2);
    \node [empty-box-vert, below of=dddbn2] (bottom3) {\(\vdots\)};
    \path [line] (dddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom3);
\end{tikzpicture}
\captionsetup{width=.75\linewidth}
\caption{Filtering errors}
\label{fig:error-filtration}
\end{figure}

@@

\begin{breakablealgorithm}
  \caption{\(K\)-\textit{compensated de Casteljau algorithm.}}
  \label{alg:k-comp-de-casteljau}

@@

@@

\begin{breakablealgorithm}
  \caption{\textit{EFT of the sum of two floating point numbers with a FMA.}}
  \label{alg:two-prod-fma}
